Parameter precision in economic growth models inspired by Ecological Economics

### 2015-10-04 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Editing introduction.

The Cobb-Douglas production function 
is the canonical representation of indexed economic output ($y$) 
as a function of 
indexed labor~($l$), 
indexed capital stock~($k$), and 
an additional exogenous, time-dependent term~($A$).
This production function can be expressed as
%
\begin{equation} \label{eq:CD}
  y = \theta A k^\alpha_k l^\alpha_l \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
\end{equation}
%
where 
$y \equiv Y/Y_{0}$,
$\theta$ is a scale parameter,
e is the base of the natural logarithm, 
$\lambda$ is represents the pace of technological progress,
$t$ is time (typically measured in years),
$k \equiv K/K_{0}$, 
$l \equiv L/L_{0}$, 
$Y$ is represented by GDP, 
$K$ is expressed in currency units, 
$L$ is expressed in workers or work-hours/year, and
0 subscripts indicate values at an initial year.
The parameters $\alpha_k$ and $\alpha_l$ are output elasticities
that indicate the marginal productivity of 
capital and labor in the economy, respectively.
Typically, the constraint $\alpha_k + \alpha_l = 1$ is assumed, 
indicating constant returns to scale.%
  \footnote{Dimensionless, indexed quantities are represented by lower-case symbols 
  ($y$, $k$, $l$, and later $e$), 
  and dimensional quantities are represented by upper-case symbols 
  ($Y$, $K$, $L$, and later $E$). 
  Model parameters are represented by Greek letters
  ($\theta$, $\lambda$, $\alpha_k$, $\alpha_l$, 
  later $\alpha_e$, $\delta_1$, $\delta$, $\sigma_1$, and $\sigma$).}

>>>>

The Cobb-Douglas production function 
is the canonical representation of indexed economic output ($y$) 
as a function of indexed factors of production~($x_1$, $x_2$, and $x_3$) and 
an additional exogenous, time-dependent term~($A$).
This production function can be expressed as
%
\begin{equation} \label{eq:CD}
  y = \theta A \, {x_1}^{\alpha_1} \, {x_2}^{\alpha_2} \, {x_3}^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
\end{equation}
%
where 
$y \equiv Y/Y_{0}$,
$\theta$ is a scale parameter,
e is the base of the natural logarithm, 
$\lambda$ is represents the pace of technological progress,
$t$ is time measured in years,
$x_1 \equiv K/K_{0}$, 
$x_2 \equiv L/L_{0}$, 
$Y$ is economic output represented by GDP, 
$K$ is capital stock expressed in currency units, 
$L$ is labor expressed in workers or work-hours/year, and
0 subscripts indicate values at an initial year.
The parameters $\alpha_k$ and $\alpha_l$ are output elasticities
that indicate the marginal productivity of 
capital and labor in the economy, respectively.
Typically, the constraint $\alpha_k + \alpha_l = 1$ is assumed, 
indicating constant returns to scale.%
  \footnote{Dimensionless, indexed quantities are represented by lower-case symbols 
  ($y$, $k$, $l$, and later $e$), 
  and dimensional quantities are represented by upper-case symbols 
  ($Y$, $K$, $L$, and later $E$). 
  Model parameters are represented by Greek letters
  ($\theta$, $\lambda$, $\alpha_k$, $\alpha_l$, 
  later $\alpha_e$, $\delta_1$, $\delta$, $\sigma_1$, and $\sigma$).}
